Paper 1

### 2022-07-07 scripts/Paper 1.Rmd
ET

input <- input %>% select(xlDateTime, Fe, Fg_Av, Fh, Fld, Flu, Fn, Fsu, Fsd, Precip, RH, Sws, Ta, Ts, VPD, Wd_SONIC_Av, Ws_SONIC_Av,ER_LT_all, GPP_LT,GPP_SOLO, NEE_LT, ET ) # select met variables (add more as needed)
colnames(input) <- c('Timestamp', 'LE', 'G', 'H', 'LWin', 'LWout', 'NETRAD', 'SWout', 'SWin', 'Precip', 'RH', 'SWC', 'Ta', 'Ts', 'VPD', 'WD', 'WS', 'ER_LT', 'GPP_LT', 'GPP_SOLO', 'NEE_LT', 'ET')

@@

input$jday <-yday(input$Timestamp) # add jday
input$Year <- year(input$Timestamp) # extract year
input$Year <- as.factor(input$Year) # convert year from integer to factor
input$month <- month(as.POSIXct(input$Timestamp)) # extract month
input$month <- as.factor(input$month)
input$ET <-as.numeric(input$ET)
```

@@

```{r create daily mean dataframe, include=FALSE}
# add variables to this daily df as needed
input.daily <- input %>%
  drop_na(Timestamp) %>% # some NAs in the Timestamp for some reason. Need to look into
  ddply(c("Year", "jday", "month"), summarise,
        Precip = sum(Precip, na.rm = TRUE),
        SWin = sum(SWin),
        Ta.mean = mean(Ta, na.rm = TRUE),
        Ta.max = max(Ta, na.rm = TRUE),
        Ta.min = min(Ta, na.rm = TRUE),
        Ts.mean = mean(Ts, na.rm = TRUE),
        Ts.max = max(Ts, na.rm = TRUE),
        Ts.min = min(Ts, na.rm = TRUE),
        SWC = mean(SWC, na.rm = TRUE),
        RH = mean(RH, na.rm = TRUE),
        VPD = mean(VPD, na.rm = TRUE),
        ET = mean(ET, na.rm = TRUE) * 86400,
        NEE_LT = mean(NEE_LT, na.rm = TRUE), #daily average umol m-2 s-1
        ER_LT = mean(ER_LT, na.rm = TRUE),
        GPP_LT = mean(GPP_LT, na.rm = TRUE)) %>%
  mutate(NEE_LT.gC = gofC.f(NEE_LT),  #converts to daily total NEE in g C CO2
         ER_LT.gC = gofC.f(ER_LT),
         GPP_LT.gC = gofC.f(GPP_LT))

@@

```
```{r, fig.width=13, fig.height=5}
group.colour <- c("19/20" = "#E69F00", "20/21" = "#009E73", "21/22" ="#D55E00")

(ET.p <- ggplot(input.rearranged, aes(x = dayssinceJun1, y = ET, group = GSYear)) +
  geom_line(aes(color = GSYear), size = 1)+
    scale_color_manual(values = group.colour) +
 # scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  xlab("Days since June 1st")+
   ylab("ET (mm/day)")+
  theme_classic())+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14))
```

@@

```{r VPD, echo=FALSE, message = FALSE, fig.width = 9, fig.height = 4}

(VPD.p <- ggplot(input.rearranged, aes(x = dayssinceJun1, y = VPD, group = GSYear)) +
  geom_line(aes(color = GSYear), size = 1)+
    scale_color_manual(values = group.colour) +
 # scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  xlab("Days since June 1st")+
   ylab("VPD (kPa")+
  theme_classic())+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14))

@@

```{r, echo=FALSE, message = FALSE, fig.width = 7, fig.height = 4}

@@

```{r}
GPP.summary <- input.rearranged %>% ddply(c("GSYear", "season"), summarise,
                                       monthly.sum = sum(GPP_LT.gC))
GPP.summary$season <- factor(GPP.summary$season, levels=c("Winter", "Spring", "Summer", "Autumn"))

GPP.summary <- input.rearranged %>% ddply(c("GSYear"), summarise,
                                       monthly.sum = sum(GPP_LT.gC))
#GPP.summary$month.name <- factor(GPP.summary$month.name, levels=c("Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", #"Apr", "May"))

>>>>

input <- input %>% select(xlDateTime, Fe, Fg_Av, Fh, Fld, Flu, Fn, Fsu, Fsd, Precip, RH, Sws, Ta, Ts, VPD, Wd_SONIC_Av, Ws_SONIC_Av,ER_LT_all, GPP_LT,GPP_SOLO, NEE_LT, ET_EF ) # select met variables (add more as needed)
colnames(input) <- c('Timestamp', 'LE', 'G', 'H', 'LWin', 'LWout', 'NETRAD', 'SWout', 'SWin', 'Precip', 'RH', 'SWC', 'Ta', 'Ts', 'VPD', 'WD', 'WS', 'ER_LT', 'GPP_LT', 'GPP_SOLO', 'NEE_LT', 'ET')

@@

input$jday <-yday(input$Timestamp) # add jday
input$Year <- year(input$Timestamp) # extract year
input$Year <- as.factor(input$Year) # convert year from integer to factor
input$month <- month(as.POSIXct(input$Timestamp)) # extract month
input$month <- as.factor(input$month)
```

@@

```{r create daily mean dataframe, include=FALSE}
# add variables to this daily df as needed
input.daily <- input %>%
  drop_na(Timestamp) %>% # some NAs in the Timestamp for some reason. Need to look into
  ddply(c("Year", "jday", "month"), summarise,
        Precip = sum(Precip, na.rm = TRUE),
        SWin = sum(SWin),
        Ta.mean = mean(Ta, na.rm = TRUE),
        Ta.max = max(Ta, na.rm = TRUE),
        Ta.min = min(Ta, na.rm = TRUE),
        Ts.mean = mean(Ts, na.rm = TRUE),
        Ts.max = max(Ts, na.rm = TRUE),
        Ts.min = min(Ts, na.rm = TRUE),
        SWC = mean(SWC, na.rm = TRUE),
        RH = mean(RH, na.rm = TRUE),
        VPD = mean(VPD, na.rm = TRUE),
        ET = mean(ET, na.rm = TRUE),
        NEE_LT = mean(NEE_LT, na.rm = TRUE), #daily average umol m-2 s-1
        ER_LT = mean(ER_LT, na.rm = TRUE),
        GPP_LT = mean(GPP_LT, na.rm = TRUE)) %>%
  mutate(NEE_LT.gC = gofC.f(NEE_LT),  #converts to daily total NEE in g C CO2
         ER_LT.gC = gofC.f(ER_LT),
         GPP_LT.gC = gofC.f(GPP_LT))

@@

@@

```{r VPD, echo=FALSE, message = FALSE, fig.width = 9, fig.height = 4}
(VPD.p <- ggplot(input.rearranged, aes(x = dayssinceJun1, y = VPD, group = GSYear)) +
  geom_line(aes(color = GSYear), size = 1)+
    scale_color_manual(values = group.colour) +
 # scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  xlab("Days since June 1st")+
   ylab("VPD (kPa")+
  theme_classic())+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14))

@@

```{r, echo=FALSE, message = FALSE, fig.width = 7, fig.height = 4}
group.colour <- c("19/20" = "#E69F00", "20/21" = "#009E73", "21/22" ="#D55E00")

@@

```{r}
GPP.summary <- input.rearranged %>% ddply(c("GSYear", "season"), summarise,
                                       monthly.sum = sum(GPP_LT.gC))

GPP.summary <- input.rearranged %>% ddply(c("GSYear"), summarise,
                                       monthly.sum = sum(GPP_LT.gC))
#GPP.summary$month.name <- factor(GPP.summary$month.name, levels=c("Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar", #"Apr", "May"))
GPP.summary$season <- factor(GPP.summary$season, levels=c("Winter", "Spring", "Summer", "Autumn"))
